Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2014-01-03 paper.tex
More MinimaLT

@@

When establishing a single TLS connection, two hosts have to go through a TCP three-way handshake

>>>>

In the original MinimaLT paper, a directory service is introduced to deal with the exchange of hosts information. We will not cover that part but will rather explain how MinimaLT can be used along with the Namecoin blockchain.

\subsection{Changes to make in Namecoin to make it play nicely with MinimaLT}

We will see that we would like to have DNS lookups that return : the IP Address, UDP port, key, ephemeral key.

Hence, we want to change the namecoin structure to be.

@@

When establishing a single TLS connection, two hosts have to go through a TCP three-way handshake and then can start the TLS handshake which requires 4 more RTT. Thankfully MinimaLT attempts to fix that and does perform a cryptographic handshake in \emph{less time than unencrypted TCP}.
